Viscous Transport in Eroding Porous Media

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There is a zoom windows of
the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
they are taken from the bottom middle frame of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
%\begin{figure}[H]
%\begin{center}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
%  tracers around the bodies. Since we use a Barycentric quadrature rule
 % and the fourth order Runge Kutta method, the tracers can be very close
 % to but not penetrate the bodies.}
%\end{center}
%\end{figure}
{\color{red}

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous 
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
}

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort}(c),
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort}(c)
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
are splitted by two close bodies.
}

@@

>>>>

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There is a zoom windows of
the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
they are taken from the bottom middle frame of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
%\begin{figure}[H]
%\begin{center}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
%  tracers around the bodies. Since we use a Barycentric quadrature rule
 % and the fourth order Runge Kutta method, the tracers can be very close
 % to but not penetrate the bodies.}
%\end{center}
%\end{figure}

@@

{\color{red}
In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous 
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
}

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
at the neighboring tracers and 
draw the pair of trajectories in the same color and 
are able to tell the neighboring trajectories will be very 
different if they are separated by bodies.
For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
are splitted by two close bodies.
}
